% 02-consortium.tex -- The Consortium
\chapter{The Consortium}
\label{ch:consortium}

% ====================================================================
\section{Consortium Overview}
\label{sec:consortium-overview}

The Digital Finance network is built on a multi-sector partnership model that
unites leading universities, major financial institutions, innovative SMEs,
international regulatory bodies, and applied-research centers.  Together, these
organizations provide doctoral candidates with a training environment that
bridges academic rigor and industry relevance.

\begin{highlightbox}
\textbf{19 partners across 11 European countries} collaborate to deliver
doctoral training in digital finance, combining expertise in AI, data science,
blockchain, sustainable finance, and financial regulation.
\end{highlightbox}

\vspace{4pt}

\noindent The consortium spans the following countries and institutions:

\vspace{4pt}

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}l X@{}}
  \toprule
  \textbf{Country} & \textbf{Partners} \\
  \midrule
  Netherlands   & University of Twente (Coordinator) \\
  Austria       & WU Vienna, Raiffeisen Bank International \\
  Germany       & Deutsche Bank, Fraunhofer, RPTU Kaiserslautern-Landau, ECB \\
  Romania       & ASE Bucharest, Babe\c{s}-Bolyai University \\
  Switzerland   & BFH Bern, BIS \\
  Lithuania     & Kaunas University of Technology, Swedbank \\
  Italy         & University of Naples, Cardo AI \\
  Poland        & Pozna\'{n} University of Economics and Business \\
  Belgium       & EIT Digital \\
  Greece        & Athena Research Center \\
  Luxembourg    & Royalton Partners \\
  \bottomrule
\end{tabularx}
\caption{Geographic distribution of consortium partners.}
\label{tab:country-partners}
\end{table}

% ====================================================================
\section{Beneficiary Partners}
\label{sec:beneficiary-partners}

Seven universities and one SME serve as beneficiary institutions, hosting
doctoral candidates and leading research work packages.

\vspace{4pt}

\begin{longtable}{@{}p{28mm} p{48mm} p{14mm} p{48mm}@{}}
  \toprule
  \textbf{Logo} & \textbf{Institution} & \textbf{Country} & \textbf{Role} \\
  \midrule
  \endhead
  \partnerlogo{UTW}
    & University of Twente
    & NL
    & Coordinator; AI for finance, quantitative methods \\[6pt]
  \partnerlogo{WU}
    & WU Vienna
    & AT
    & Computational finance, risk management \\[6pt]
  \partnerlogo{UNA}
    & University of Naples Federico~II
    & IT
    & Sustainable finance, insurance \\[6pt]
  \partnerlogo{KUT}
    & Kaunas University of Technology
    & LT
    & Sustainable finance, Baltic financial markets \\[6pt]
  \partnerlogo{ASE}
    & ASE Bucharest
    & RO
    & Digital banking, blockchain applications \\[6pt]
  \partnerlogo{BBU}
    & Babe\c{s}-Bolyai University
    & RO
    & Data science, financial data space \\[6pt]
  \partnerlogo{CAR}
    & Cardo AI
    & IT
    & AI-driven credit analytics (SME) \\[6pt]
  \partnerlogo{POZ}
    & Pozna\'{n} University of Economics and Business
    & PL
    & Quantitative finance \\
  \bottomrule
\end{longtable}

% ====================================================================
\section{Associated Partners}
\label{sec:associated-partners}

Eleven associated partners complement the consortium with specialized research
infrastructure, industry expertise, regulatory perspectives, and international
policy insights.

\subsection*{Academic and Research Institutions}

\begin{description}[leftmargin=0pt, labelindent=0pt, font=\sffamily\bfseries\color{mscaDarkBlue}]
  \item[BFH Bern (CH)]
    Bern University of Applied Sciences---fintech innovation, blockchain
    research, and explainable AI.

  \item[RPTU Kaiserslautern-Landau (DE)]
    Rheinland-Pf\"alzische Technische Universit\"at---financial engineering
    and computational methods.

  \item[Athena Research Center (EL)]
    Greece's leading applied-research institute, contributing expertise in NLP,
    knowledge graphs, and AI research secondments.

  \item[Fraunhofer (DE)]
    Europe's largest organization for applied research, providing access to
    advanced computing infrastructure and industry collaboration networks.

  \item[EIT Digital (BE)]
    The digital innovation arm of the European Institute of Innovation and
    Technology, facilitating pan-European entrepreneurship and technology transfer.
\end{description}

\subsection*{Financial Institutions}

\begin{description}[leftmargin=0pt, labelindent=0pt, font=\sffamily\bfseries\color{mscaDarkBlue}]
  \item[Deutsche Bank (DE)]
    A global financial institution offering access to trading platforms,
    quantitative research infrastructure, and regulatory compliance frameworks.

  \item[Raiffeisen Bank International (AT)]
    A major Central European banking group with deep experience in retail and
    corporate banking innovation across multiple markets.

  \item[Swedbank (LT)]
    One of the largest banking groups in the Nordic-Baltic region, contributing
    expertise in Nordic-Baltic banking, compliance, and digital payments.
\end{description}

\subsection*{SME}

\begin{description}[leftmargin=0pt, labelindent=0pt, font=\sffamily\bfseries\color{mscaDarkBlue}]
  \item[Royalton Partners (LU)]
    An investment firm focused on quantitative strategies and alternative
    data, providing an entrepreneurial research environment for DC projects.
\end{description}

\subsection*{International Organizations}

\begin{description}[leftmargin=0pt, labelindent=0pt, font=\sffamily\bfseries\color{mscaDarkBlue}]
  \item[European Central Bank --- ECB (DE)]
    The central bank for the euro area, offering unique perspectives on monetary
    policy, financial stability, and digital currency design.

  \item[Bank for International Settlements --- BIS (CH)]
    The principal center for international central bank cooperation, contributing
    expertise on payment systems, macrofinancial data, and global regulatory
    standards.
\end{description}

% ====================================================================
\section{Partner Logo Grid}
\label{sec:logo-grid}

\begin{center}
\vspace{4pt}
% Row 1 -- Beneficiaries (1-5)
\partnerlogo{UTW}\hspace{4mm}%
\partnerlogo{WU}\hspace{4mm}%
\partnerlogo{UNA}\hspace{4mm}%
\partnerlogo{KUT}\hspace{4mm}%
\partnerlogo{ASE}

\vspace{6mm}

% Row 2 -- Beneficiaries (6-8) + Associated (1-2)
\partnerlogo{BBU}\hspace{4mm}%
\partnerlogo{CAR}\hspace{4mm}%
\partnerlogo{POZ}\hspace{4mm}%
\partnerlogo{BFH}\hspace{4mm}%
\partnerlogo{RPTU}

\vspace{6mm}

% Row 3 -- Associated (3-7)
\partnerlogo{ARC}\hspace{4mm}%
\partnerlogo{Fraunhofer}\hspace{4mm}%
\partnerlogo{EIT Digital}\hspace{4mm}%
\partnerlogo{Deutsche Bank}\hspace{4mm}%
\partnerlogo{Raiffeisen}

\vspace{6mm}

% Row 4 -- Associated (8-11)
\partnerlogo{Swedbank}\hspace{4mm}%
\partnerlogo{Royalton}\hspace{4mm}%
\partnerlogo{ECB}\hspace{4mm}%
\partnerlogo{BIS}
\vspace{4pt}
\end{center}
