% 07-transferable-skills.tex -- Transferable Skills
\chapter{Transferable Skills}
\label{ch:transferable-skills}

Beyond scientific expertise, successful researchers need skills in
communication, project management, ethics, and professional development.  The
program offers sixteen transferable-skill modules organized in four groups.
These modules are non-credit-bearing workshops and seminars; participation is
certified by attendance.

\textit{Note: Delivery formats and durations shown below are indicative. Final scheduling is confirmed by the Training Committee for each academic year.}

% ====================================================================
\section{Group A: Research Skills}
\label{sec:ts-research}

\begin{description}[style=nextline, leftmargin=10pt,
  font=\sffamily\bfseries\color{mscaDarkBlue}]

  \item[TS-01\quad Scientific Writing and Publishing \hfill \normalfont\itshape Workshop, 2 days]
    Participants learn to structure journal articles, navigate the peer-review
    process, and develop a productive writing practice.  The workshop covers
    abstract and introduction drafting, responding to referee reports, and
    selecting appropriate outlets for digital finance research.

  \item[TS-02\quad Research Methodology and Design \hfill \normalfont\itshape Workshop, 2 days]
    Students develop the ability to formulate research questions, choose
    appropriate empirical or theoretical methods, and design studies that meet
    the standards of rigor expected in top-tier finance and computer science
    venues.

  \item[TS-03\quad Data Management and Open Science \hfill \normalfont\itshape Online, 1 day]
    Participants learn best practices for data management plans, FAIR data
    principles, open-access publishing, and the responsible sharing of code and
    datasets under European open-science guidelines.

  \item[TS-04\quad Literature Review Techniques \hfill \normalfont\itshape Workshop, 1 day]
    Students master systematic and scoping review methods, reference management
    tools, and strategies for staying current with the rapidly growing digital
    finance literature.
\end{description}

% ====================================================================
\section{Group B: Professional Development}
\label{sec:ts-professional}

\begin{description}[style=nextline, leftmargin=10pt,
  font=\sffamily\bfseries\color{mscaDarkBlue}]

  \item[TS-05\quad Project Management for Researchers \hfill \normalfont\itshape Workshop, 2 days]
    Participants learn to plan, execute, and monitor research projects using
    agile and milestone-based approaches.  The workshop covers time management,
    risk identification, and stakeholder communication in the context of
    doctoral research.

  \item[TS-06\quad Entrepreneurship and Innovation \hfill \normalfont\itshape Workshop, 2 days]
    Students explore pathways from research to market---lean-startup methods,
    business model canvases, and technology transfer mechanisms.  Guest
    speakers from consortium SMEs share their experience translating academic
    ideas into fintech products.

  \item[TS-07\quad Intellectual Property Rights \hfill \normalfont\itshape Seminar, half-day]
    Participants receive a practical overview of intellectual property
    protection---patents, software licensing, trade secrets---and learn how IP
    considerations affect academic publishing and industry collaboration.

  \item[TS-08\quad Job Applications and Career Planning \hfill \normalfont\itshape Workshop, 1 day]
    Students prepare for the academic and industry job markets.  The workshop
    covers CV and cover-letter writing, interview preparation, negotiation
    strategies, and long-term career planning for PhDs in finance and
    technology.
\end{description}

% ====================================================================
\section{Group C: Communication}
\label{sec:ts-communication}

\begin{description}[style=nextline, leftmargin=10pt,
  font=\sffamily\bfseries\color{mscaDarkBlue}]

  \item[TS-09\quad Academic Presentation Skills \hfill \normalfont\itshape Workshop, 2 days]
    Participants refine their ability to present research at conferences,
    seminars, and industry events.  The workshop combines structured feedback
    sessions with video analysis, covering slide design, narrative structure,
    and handling Q\&A sessions.

  \item[TS-10\quad Science Communication \hfill \normalfont\itshape Workshop, 1 day]
    Students learn to communicate complex research findings to non-specialist
    audiences---policymakers, journalists, and the general public---through
    blog posts, social media, and press interactions.

  \item[TS-11\quad Grant Writing \hfill \normalfont\itshape Workshop, 1 day]
    Participants practice writing competitive funding proposals, with a focus
    on ERC Starting Grants, MSCA Postdoctoral Fellowships, and national
    funding schemes.  Exercises include drafting project abstracts and budget
    justifications.

  \item[TS-12\quad Networking and Collaboration \hfill \normalfont\itshape Mentoring, ongoing]
    Students build professional networks through structured mentoring sessions,
    cross-WP collaboration opportunities, and guidance on establishing
    productive research partnerships across institutions and sectors.
\end{description}

% ====================================================================
\section{Group D: Ethics, Diversity, and Society}
\label{sec:ts-ethics}

\begin{description}[style=nextline, leftmargin=10pt,
  font=\sffamily\bfseries\color{mscaDarkBlue}]

  \item[TS-13\quad Research Ethics and Integrity \hfill \normalfont\itshape Online, half-day]
    Participants complete training on research integrity, covering plagiarism
    prevention, data fabrication and falsification, authorship ethics, and the
    responsible conduct of research with human subjects and sensitive financial
    data.

  \item[TS-14\quad Gender Equality and Diversity \hfill \normalfont\itshape Seminar, half-day]
    Students explore how gender and diversity considerations shape research
    design, team dynamics, and career outcomes in finance and technology.
    The seminar includes the consortium's Gender Equality Plan and its
    implementation in practice.

  \item[TS-15\quad Responsible Innovation \hfill \normalfont\itshape Seminar, half-day]
    Participants examine the societal implications of digital finance
    technologies---financial inclusion, algorithmic discrimination, digital
    divides---and learn to integrate responsibility considerations into
    technology design from the earliest stages.

  \item[TS-16\quad Interdisciplinary Thinking \hfill \normalfont\itshape Workshop, 1 day]
    Students practice methods for working across disciplinary boundaries,
    drawing on case studies from the consortium's own cross-WP collaborations.
    The workshop builds skills in translating concepts, resolving
    methodological conflicts, and co-authoring with researchers from different
    fields.
\end{description}
