% 08-secondments.tex -- Secondments
\chapter{Secondments}
\label{ch:secondments}

% ====================================================================
\section{Secondment Program Structure}
\label{sec:secondment-structure}

International secondments are a defining feature of the MSCA Industrial
Doctoral Network.  Every doctoral candidate spends a substantial period working
at institutions other than their home university, gaining exposure to different
research cultures, industry practices, and regulatory environments.

The program follows a dual secondment model.  Each DC undertakes a research
center secondment of up to six months at one of the consortium's associated
research partners, focusing on advanced methodological training and access to
specialized infrastructure.  In addition, each DC completes an industry
secondment of up to eighteen months at a corporate partner, SME, or
international organization, where research is conducted in a production
environment under joint academic-industry supervision.

Secondments are integrated with the five research work packages.  Each
placement is designed to advance the doctoral candidate's thesis while
providing skills and perspectives that cannot be acquired at the home
institution alone.  Supervisory arrangements, research objectives, and
deliverables are agreed before each secondment begins.

\vspace{8pt}

% --- TikZ Secondment Timeline ---
\begin{center}
\begin{tikzpicture}[x=28mm, y=10mm]
  % Axis
  \draw[-{Stealth[length=3mm]}, thick, mscaGrey]
    (0,0) -- (4.5,0)
    node[right, font=\sffamily\small\color{mscaGrey}] {Time};

  % Year labels
  \foreach \y/\label in {0.5/Year 1, 1.5/Year 2, 2.5/Year 3, 3.5/Year 4} {
    \node[below=2mm, font=\sffamily\footnotesize\color{mscaGrey}] at (\y,0) {\label};
    \draw[mscaGrey!50] (\y-0.5, -0.1) -- (\y-0.5, 0.1);
  }
  \draw[mscaGrey!50] (4, -0.1) -- (4, 0.1);

  % Home institution (blue)
  \fill[mscaMediumBlue!60] (0, 0.4) rectangle (1.4, 1.0);
  \fill[mscaMediumBlue!60] (2.6, 0.4) rectangle (4.0, 1.0);
  \node[font=\sffamily\scriptsize\color{white}] at (0.7, 0.7)
    {Home institution};
  \node[font=\sffamily\scriptsize\color{white}] at (3.3, 0.7)
    {Home institution};

  % Research center secondment (green)
  \fill[green!40!mscaMediumBlue] (1.4, 0.4) rectangle (2.0, 1.0);
  \node[font=\sffamily\scriptsize\color{white}] at (1.7, 0.7)
    {Research};

  % Industry secondment (gold)
  \fill[mscaAccentGold] (2.0, 0.4) rectangle (2.6, 1.0);
  \node[font=\sffamily\scriptsize\color{white}] at (2.3, 0.7)
    {Industry};

  % Legend
  \fill[mscaMediumBlue!60]       (0.2, -1.0) rectangle (0.5, -0.75);
  \fill[green!40!mscaMediumBlue] (1.7, -1.0) rectangle (2.0, -0.75);
  \fill[mscaAccentGold]          (3.0, -1.0) rectangle (3.3, -0.75);
  \node[right, font=\sffamily\scriptsize] at (0.5, -0.875) {Home institution};
  \node[right, font=\sffamily\scriptsize] at (2.0, -0.875) {Research center};
  \node[right, font=\sffamily\scriptsize] at (3.3, -0.875) {Industry};
\end{tikzpicture}
\end{center}

\vspace{4pt}

\begin{highlightbox}
\textbf{Note:} The timeline above is illustrative.  The exact timing and
duration of each secondment varies by doctoral candidate and is agreed with the
supervisory team.
\end{highlightbox}

% ====================================================================
\section{What to Expect}
\label{sec:secondment-expect}

During a secondment, doctoral candidates receive co-supervision from a local
mentor at the host institution in addition to their primary supervisor.  The
consortium provides travel and relocation support as well as the standard MSCA
living and mobility allowances, which cover housing, insurance, and daily
expenses.

Secondments are designed to build competencies that complement home-institution
research: hands-on experience with production-scale systems at industry
partners, access to specialized laboratories and datasets at research centers,
and exposure to regulatory and policy perspectives at international
organizations.  All activities and outputs contribute directly to the doctoral
thesis.

% ====================================================================
\section{What Secondment Hosts Provide}
\label{sec:secondment-hosts}

\textbf{Research Centers (Athena Research Center, EIT Digital, Fraunhofer, ECB, BIS).}\quad
Research center hosts offer access to specialized computing labs, curated
research datasets, and multidisciplinary teams.  Doctoral candidates join
active research groups, participate in internal seminars, and benefit from
infrastructure---such as GPU clusters and secure data rooms---that may not be
available at their home institution.

\textbf{Corporations (Swedbank, Deutsche Bank, Raiffeisen Bank International).}\quad
Corporate hosts embed doctoral candidates in technology, risk, or data science
teams that operate production-scale financial systems.  Researchers gain
first-hand experience with industry workflows, real-time data pipelines, and
regulatory compliance processes while receiving mentorship from senior
practitioners.

\textbf{SMEs (Royalton Partners).}\quad
SME hosts provide an entrepreneurial environment where doctoral candidates
contribute directly to product development and innovation.  Researchers
experience the full cycle from prototype to deployment in a fast-moving
fintech setting, building skills in agile development and commercial
awareness.

\vspace{4pt}
{\itshape\color{mscaGrey}[REAL QUOTES FROM SECONDMENT HOSTS TO BE COLLECTED]}

\vspace{8pt}

% --- Secondment Destinations Table ---
\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{}l l X@{}}
  \toprule
  \textbf{Type} & \textbf{Duration} & \textbf{Destinations} \\
  \midrule
  Research Center      & Up to 6 months    & Athena Research Center, EIT Digital,
                                             Fraunhofer, ECB, BIS \\
  Industry (Corporate) & Up to 18 months   & Swedbank, Deutsche Bank, Raiffeisen
                                             Bank International \\
  Industry (SME)       & Up to 18 months   & Royalton Partners \\
  \bottomrule
\end{tabularx}
\caption{Secondment destinations by type and duration.}
\label{tab:secondment-destinations}
\end{table}
