% 09-events-2026.tex -- 2026 Training Events
\chapter{2026 Training Events}
\label{ch:events-2026}

The MSCA Digital Finance network organises a series of training events throughout
2026, ranging from intensive workshops and technical training weeks to an
end-of-year research symposium.  This chapter documents the events that have
already taken place and previews those still to come.  All events are open to
external PhD students; registration details are published on the program website.

% ====================================================================
% PAST EVENT: Bucharest
% ====================================================================
\newpage
\eventpage
  {Practice of Digital Finance Workshop}
  {15--16 January 2026}
  {Bucharest, Romania}
  {Bucharest University of Economic Studies (ASE)}
  {The workshop brought together doctoral candidates and senior researchers to
   examine practical applications of digital finance in Central and Eastern
   European banking.  Sessions covered topics including digital payments,
   AI-driven compliance, and regulatory technology.
   \emph{[COORDINATOR TO PROVIDE: attendance figures]}}
  {\begin{description}[leftmargin=0pt, labelindent=0pt, font=\sffamily\bfseries\color{mscaDarkBlue}]
   \item[Day 1 --- 15 January]
     Opening ceremony and welcome by ASE Bucharest.  Keynote address on the
     digital banking transformation in Central and Eastern Europe.  Three
     parallel technical sessions covered topics including digital payments,
     AI-driven compliance, and regulatory technology.
     \emph{[COORDINATOR TO PROVIDE: session titles]}
     The day concluded with a networking dinner
     \emph{[COORDINATOR TO PROVIDE: dinner venue]}.
   \item[Day 2 --- 16 January]
     Workshop sessions on applied topics in digital finance and banking
     compliance.  An industry panel featured
     industry representatives \emph{[COORDINATOR TO VERIFY: panel participants]}
     who discussed practical challenges of deploying technology in compliance
     workflows.  Closing remarks summarised key findings and outlined follow-up
     activities.
   \end{description}}
  {}

\begin{tcolorbox}[colback=mscaLightBlue, colframe=mscaMediumBlue, title={Key Outcomes}]
\begin{itemize}[nosep]
  \item \emph{[COORDINATOR TO PROVIDE: Key takeaway 1]}
  \item \emph{[COORDINATOR TO PROVIDE: Key takeaway 2]}
  \item \emph{[COORDINATOR TO PROVIDE: Key takeaway 3]}
\end{itemize}
\end{tcolorbox}

% ====================================================================
% UPCOMING EVENT 1: Mid-Year Technical Training Week
% ====================================================================
\newpage
\eventpage
  {Mid-Year Technical Training Week}
  {May/June 2026 (exact dates TBD)}
  {Location TBD}
  {Host Institution TBD}
  {An intensive five-day training week focusing on advanced computational
   methods for digital finance research.  Topics are expected to include deep
   learning for financial time series, large language models in regulatory
   analysis, and hands-on coding laboratories.  Further details will be
   announced in spring 2026.}
  {Program details to be confirmed.}
  {}

\begin{tcolorbox}[colback=mscaLightGrey, colframe=mscaGrey, arc=2mm]
\centering\sffamily\large\color{mscaGrey}
Details to be announced.  Visit \url{https://www.digital-finance-msca.com/} for updates.
\end{tcolorbox}

% ====================================================================
% UPCOMING EVENT 2: Autumn Advanced Topics Workshop
% ====================================================================
\newpage
\eventpage
  {Autumn Advanced Topics Workshop}
  {October 2026 (exact dates TBD)}
  {Location TBD}
  {Host Institution TBD}
  {A two-day workshop dedicated to advanced research topics in digital
   finance.  Anticipated themes include decentralised finance risk modelling,
   central bank digital currencies, and quantitative methods for climate
   finance.  The workshop will feature both invited lectures and doctoral
   candidate presentations.}
  {Program details to be confirmed.}
  {}

\begin{tcolorbox}[colback=mscaLightGrey, colframe=mscaGrey, arc=2mm]
\centering\sffamily\large\color{mscaGrey}
Details to be announced.  Visit \url{https://www.digital-finance-msca.com/} for updates.
\end{tcolorbox}

% ====================================================================
% UPCOMING EVENT 3: Year-End Research Symposium
% ====================================================================
\newpage
\eventpage
  {Year-End Research Symposium}
  {December 2026 (exact dates TBD)}
  {Location TBD}
  {Host Institution TBD}
  {The annual research symposium brings together all doctoral candidates,
   supervisors, and advisory board members to review progress, present
   research results, and plan the final year of the program.  External
   researchers are invited to attend and present their work in a dedicated
   open session.}
  {Program details to be confirmed.}
  {}

\begin{tcolorbox}[colback=mscaLightGrey, colframe=mscaGrey, arc=2mm]
\centering\sffamily\large\color{mscaGrey}
Details to be announced.  Visit \url{https://www.digital-finance-msca.com/} for updates.
\end{tcolorbox}
