% 11-how-to-participate.tex -- How to Participate
\chapter{How to Participate}
\label{ch:how-to-participate}

% ====================================================================
\section{Who Can Participate}
\label{sec:who-can-participate}

The Digital Finance training program is open to \textbf{all European PhD
students and early-career researchers}, not only those holding funded positions
within the consortium.  We welcome participants from finance, computer science,
mathematics, economics, data science, and related disciplines.  There are no
nationality restrictions---researchers enrolled at any European institution are
eligible.  Participation from non-European institutions is considered on a
case-by-case basis.

% ====================================================================
\section{Registration Process}
\label{sec:registration}

Joining a training event takes four simple steps:

\begin{enumerate}[nosep]
  \item Visit the program website at
        \url{https://www.digital-finance-msca.com/}.
  \item Browse the calendar of upcoming events and select those of interest.
  \item Complete the online registration form for each event.
  \item Receive a confirmation email with joining instructions and logistics.
\end{enumerate}

Early registration is strongly encouraged, as several events have limited
capacity and places are allocated on a first-come, first-served basis.

% ====================================================================
\section{Costs and Support}
\label{sec:costs}

Most training events organised by the consortium are offered \textbf{free of
charge} to external participants.  Where a modest registration fee applies,
this is clearly indicated on the event page.

Limited travel support may be available for participants from institutions in
widening countries or for those facing financial constraints.  Interested
researchers should contact the coordinator before the registration deadline to
inquire about funding options.  ECTS credit recognition can be arranged through
the participant's home institution upon request.

% ====================================================================
\section{Contact}
\label{sec:contact}

For general inquiries about the training program, registration, or travel
support, please contact the project coordinator:

\begin{center}
\begin{tcolorbox}[colback=mscaLightBlue, colframe=mscaMediumBlue, arc=2mm,
  width=0.8\textwidth, boxrule=0.5pt,
  left=6mm, right=6mm, top=4mm, bottom=4mm]
\centering
{\large\sffamily\bfseries\color{mscaDarkBlue} Prof.\ Dr.\ Joerg R.\ Osterrieder}\\[4pt]
{\sffamily Project Coordinator}\\[2pt]
{\sffamily University of Twente, The Netherlands}\\[8pt]
{\sffamily\color{mscaMediumBlue} \url{https://www.digital-finance-msca.com/}}\\[2pt]
{\sffamily\color{mscaMediumBlue} \emph{[COORDINATOR TO PROVIDE: contact email]}}\\[10pt]
\qrcode[height=2cm]{https://www.digital-finance-msca.com/}
\end{tcolorbox}
\end{center}
