% foreword.tex -- Coordinator's foreword
\chapter*{Foreword}
\addcontentsline{toc}{chapter}{Foreword}

Welcome to the 2026 training catalog of the MSCA Industrial Doctoral Network on
Digital Finance. This booklet presents the full scope of doctoral training activities
planned and available during the third year of our program. Our mission is to equip
the next generation of researchers with the analytical depth, technical competence,
and cross-sectoral perspective needed to address the most pressing challenges in
digital finance --- from decentralised financial systems and central bank digital
currencies to the responsible application of artificial intelligence in banking,
insurance, and capital markets.

What distinguishes this network is its breadth and integration. Nineteen
partner organisations across eleven European countries --- spanning universities,
applied-research institutes, banks, fintech firms, and regulatory bodies --- contribute
to a training environment that no single institution could provide alone. Doctoral
candidates work at the intersection of disciplines, moving between academic and
industrial settings, gaining first-hand insight into how research translates into
practice and how practice shapes the questions worth investigating.

The year 2026 marks an important phase for the network. Our first cohort of doctoral
candidates is now completing the second year of research, with individual projects
well under way and initial results taking shape. In May 2025 the project underwent
its mid-term review, a formal EU evaluation of progress at the halfway point, which
confirmed that the network is progressing well \emph{[COORDINATOR TO VERIFY: mid-term review outcome wording]}. Building on this
foundation, we have opened our training program to all external European PhD students
working in related fields, extending the reach and impact of the courses, workshops,
and summer schools described in this booklet. Industry collaboration has also deepened:
partners including Deutsche Bank, Swedbank, and Raiffeisen are contributing expertise
through research collaboration and secondment placements. In
January 2026 the network held a workshop in Bucharest, bringing together doctoral
candidates, supervisors, and industry partners for concentrated exchange on current
research themes.

I invite you to explore the pages that follow. Whether you are a doctoral candidate
within the network, an external PhD student seeking advanced training, a prospective
industry partner, or a colleague interested in collaboration, you will find detailed
information on courses, events, and opportunities for the coming year. We look forward
to welcoming you.

\vspace{12pt}

\noindent\textit{Prof.\ Dr.\ Joerg R.\ Osterrieder}\\
\noindent University of Twente \& Bern University of Applied Sciences\\
\noindent Coordinator, MSCA Digital Finance Network

\newpage
